### 2015-04-21 paper.tex
Fix boldface
Fix labels
Add K transport bar graph figure

\begin{table}[ht]
\centering
\begin{tabular}{c|c|c}
Tow speed (m/s) & $Re_D$ & $Re_c$ at $\lambda = 3$ \\ 
\hline 
0.2 & $2.2 \times 10^5$ & $4.0 \times 10^4$ \\ 
0.4 & $4.3 \times 10^5$ & $8.0 \times 10^4$ \\ 
0.6 & $6.5 \times 10^5$ & $1.2 \times 10^5$ \\ 
0.8 & $8.6 \times 10^5$ & $1.6 \times 10^5$ \\ 
1.0 & $1.1 \times 10^6$ & $2.0 \times 10^5$ \\ 
1.2 & $1.3 \times 10^6$ & $2.4 \times 10^5$ \\ 
1.4 & $1.5 \times 10^6$ & $2.8 \times 10^5$ \\
\end{tabular} 
\caption{{\textbf Test Reynolds numbers.}Turbine diameter and approximate blade 
chord Reynolds numbers corresponding to tow speeds.} \label{tab:re}
\end{table}

@@

\begin{figure}[h]
%\includegraphics[width=\textwidth]{figures/meancontquiv}
\caption{{\bf Near-Wake Mean Velocity Field.}
Mean velocity field at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and
$\lambda=3.1$.}
\label{meancontquiv}
\end{figure}

\begin{figure}[h]
%\includegraphics[width=\textwidth]{figures/k_contours}
\caption{{\bf Turbulence Kinetic Energy.}
Turbulence kinetic energy at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and
$\lambda=3.1$.}
\label{kcont}
\end{figure}

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{c|c|c}
Tow speed (m/s) & $Re_D$ & $Re_c$ at $\lambda = 3$ \\ 
\hline 
0.2 & $2.2 \times 10^5$ & $4.0 \times 10^4$ \\ 
0.4 & $4.3 \times 10^5$ & $8.0 \times 10^4$ \\ 
0.6 & $6.5 \times 10^5$ & $1.2 \times 10^5$ \\ 
0.8 & $8.6 \times 10^5$ & $1.6 \times 10^5$ \\ 
1.0 & $1.1 \times 10^6$ & $2.0 \times 10^5$ \\ 
1.2 & $1.3 \times 10^6$ & $2.4 \times 10^5$ \\ 
1.4 & $1.5 \times 10^6$ & $2.8 \times 10^5$ \\
\end{tabular} 
\caption{{\bf Test Reynolds numbers.}Turbine diameter and approximate blade 
chord Reynolds numbers corresponding to tow speeds.} \label{tab:re}
\end{table}

@@

\begin{figure}[h]
%\includegraphics[width=\textwidth]{figures/meancontquiv}
\caption{{\bf Near-Wake Mean Velocity Field.}
Mean velocity field at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and
$\lambda=3.1$.}
\label{fig:meancontquiv}
\end{figure}

\begin{figure}[h]
%\includegraphics[width=\textwidth]{figures/k_contours}
\caption{{\bf Turbulence Kinetic Energy.}
Turbulence kinetic energy at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and
$\lambda=3.1$.}
\label{fig:kcont}
\end{figure}

\begin{figure}[ht!]
\includegraphics[width=\textwidth]{figures/K_trans_bar_graph}
\caption{{\bf Mean Kinetic Energy Transport.}
Estimates for terms contributing to streamwise recovery of mean kinetic energy.}
\label{fig:Ktransport}
\end{figure}
